---
title: "Synopsis from IMDB"
author: "Anton"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center",
  error = FALSE,
  message = FALSE, 
  warning = FALSE,
  tidy = TRUE
)
```

# Loading Libraries
```{r}
library(readxl) #for reading excel file
library(rvest) #for scraping
library(dplyr) #for piping
library(RCurl) #for checking 404 of page
library(robotstxt) #for checking robotstxt
library(data.table) #for encanced data.frame
library(stringr) #for replacing matched patterns
library(stringi) #for ADCII transformation
library(tidytext) #for unnesting tokens
library(tidyverse)
library(tokenizers) #for stemming and tokenizing
library(tidyr)
library(tm)
library(topicmodels) #for LDA
library(fmsb) #for Radarchart
```

# Scraping
## Checking permissions co scrape and crawl

```{r}
#' _Check for permissions_
# rtxt <- robotstxt("https://www.imdb.com")
# rtxt$permissions
# 
# paths_allowed("https://www.imdb.com/list/ls009487211/")
```

## Getting links and URLs for movies
```{r}
#' *URLS we want to scrape from*
#' On IMDB there is a page where (almost) all the best picture nominees are listed
#' The list is however paginated so we need multiple url
  url1 <- "https://www.imdb.com/list/ls009487211/"
  url2 <- "https://www.imdb.com/list/ls009487211/?sort=list_order,asc&st_dt=&mode=detail&page=2"
  url3 <- "https://www.imdb.com/list/ls009487211/?sort=list_order,asc&st_dt=&mode=detail&page=3"
  url4 <- "https://www.imdb.com/list/ls009487211/?sort=list_order,asc&st_dt=&mode=detail&page=4"
  url5 <- "https://www.imdb.com/list/ls009487211/?sort=list_order,asc&st_dt=&mode=detail&page=5"
  
#' *Getting links for movies*
#' The Css path is ".lister-item-header a"
links_movies <- c()
  links_movies[1:100] <- read_html(url1) %>%
    html_nodes(".lister-item-header a") %>%
    html_attr("href")
  
  links_movies[101:200] <- read_html(url2) %>%
    html_nodes(".lister-item-header a") %>%
    html_attr("href")
  
  links_movies[201:300] <- read_html(url3) %>%
    html_nodes(".lister-item-header a") %>%
    html_attr("href")
  
  links_movies[301:400] <- read_html(url4) %>%
    html_nodes(".lister-item-header a") %>%
    html_attr("href")
  
  links_movies[401:472] <- read_html(url5) %>%
    html_nodes(".lister-item-header a") %>%
    html_attr("href")

#' *Creating data table*
movies <- data.table(movielink = links_movies)
  # head(movies)
  
#' *Making complete url for movie*
movies$url_movie <- NA
  movies$url_movie <- paste0("https://www.imdb.com", movies$movielink)
  
#' *Removing ?ref_* 
#' Finding location of ref in string
#' We cannot look for "?" since it is a regex, so we look for "ref"
location_ref <- c()
  for (i in 1:length(movies$url_movie)){
    cat(paste0("Loop nr.", i, ", "))
    location_ref[i] <- str_locate_all(pattern ='ref', movies$url_movie[i])
  }
#' *Removing everything after characterposition-2 to remove "/?" as well*
  for (i in 1:length(movies$url_movie)){
    cat(paste0("Loop nr.", i, ", "))
    movies$url_movie[i] <- substr(movies$url_movie[i],1,location_ref[[i]][1]-2)
  }

#' *Checking if URL exists for control*
#' Doing this only once since it takes a long time
# valid.url <- c()
#   for (i in 1:length(movies$url_movie)){
#   valid.url[i] <- url.exists(movies$url_movie[i])
#   }
# which(valid.url == FALSE)
#' Output:
#' > integer(0)
```
## Creating URLs for synopsis
The setup of the link for the synopsis and the link is very similar.
+ Movie: /title/tt6751668/
+ Synopsis: /title/tt6751668/synopsis
So we simply paste /synopsis to the end of the url_movie
```{r}
#' *Pasting url for Synopsis*
movies$url_synopsis <- NA
  movies$url_synopsis <- paste0(movies$url_movie, "plotsummary/")
#' *Checking if URL exists for control*
#' Doing this only once since it takes a long time
# valid.url_syn <- c()
#   for (i in 1:length(movies$url_synopsis)){
#   valid.url_syn[i] <- url.exists(movies$url_synopsis[i])
#   }
# which(valid.url_syn == FALSE)
#' Output:
#' > integer(0)
```

## Getting Names and year
```{r}
#' *Getting Movie Titles*
movies$title <- NA
  for (i in 1:length(movies$url_synopsis)){
  cat(paste0("Loop nr.", i, ", "))
  movies$title[i] <- read_html(movies$url_synopsis[i]) %>%
    html_nodes(".parent a") %>%
    html_text()
  }

#' *Getting Year*
movies$year <- NA
  for (i in 1:length(movies$url_synopsis)){
  cat(paste0("Loop nr.", i))
  movies$year[i] <- read_html(movies$url_movie[i]) %>%
    html_nodes("#titleYear a") %>%
    html_text()
  }
```
```{r}
write.csv(movies,"Data/movies.csv", row.names = FALSE)
rm(list = ls())
```

## Getting Synopsis
CSS: #plot-synopsis-content .ipl-zebra-list__item
```{r}
movies <- read.csv("Data/movies.csv")
movies$synopsis <- NA
for ( i in 1:length(movies$url_synopsis)){
  cat(paste0("Loop nr.", i, ", "))
  movies$synopsis[i] <- read_html(movies$url_synopsis[i]) %>%
    html_nodes("#plot-synopsis-content .ipl-zebra-list__item") %>%
    html_text()
}
movies$synopsis <- str_squish(movies$synopsis)

movies$synopsis <- movies$synopsis %>% 
  gsub(pattern = "It looks like we don't have a Synopsis for this title yet. Be the first to contribute! Just click the \"Edit page\" button at the bottom of the page or learn more in the Synopsis submission guide."
       , replacement = "empty")
```

```{r}
write.csv(movies,"Data/synopsis.csv", row.names = FALSE)
rm(list = ls())
```

## Plot
```{r}
movies <- read.csv("Data/synopsis.csv")
movies$Available <- NA

for (i in 1:length(movies$Available)){
  if (movies$synopsis[i] == "empty"){
    movies$Available[i] <- "No"
  } else {
    movies$Available[i] <- "Yes"
  }
}

plot <- as.data.frame(table(
  paste0(movies$year, ":", movies$Available)
  ))
plot$year <- plot$Var1 %>%
  gsub(pattern = ":(.*)"
       , replacement =  "") %>%
  as.numeric()
plot$Available <- plot$Var1 %>%
  gsub(pattern = "(.*):"
       , replacement =  "")

plot <- ggplot(plot, aes(fill=Available, y=Freq, x=year)) + 
    geom_bar(position="stack", stat="identity") +
    ggtitle(paste0("Total Nr of synopsis available: ", unname(table(movies$Available)[2]))) +
    xlab("") +
    theme_bw(base_size = 18) + theme(plot.title = element_text(hjust = 0.5)) +
    scale_x_continuous(breaks = seq(min(movies$year) + 1, max(movies$year) + 1, 5)) +
    scale_y_continuous("Nr of synopsis",1:12)
plot
```

### Saving Plot
```{r}
  jpeg(filename = "www/Availability of synopsis.jpeg", width = 1280, height = 720)
  plot
  dev.off()
```

```{r}
rm(list = ls())
```

# Prepping Data for Analysis

```{r}
movies <- read.csv("Data/synopsis.csv") %>% as.data.table()
```
## Tokenizing
```{r}
##' _Transforming to lower characters_
movies[, synopsis := str_to_lower(synopsis)]
##' _Removing all nonalpha characters, but keeping apostrophe’s_
movies[, synopsis := str_replace_all(synopsis, "[^[:alpha:]']", " ")]
##' _Unnest dataframe into a tidy data.table consisting of one word per row_
tidy_movies <- unnest_tokens(movies, word, synopsis, token = "words")
##' _Remove stop words_
tidy_movies <- tidy_movies %>% anti_join(stop_words)
write.csv(tidy_movies,"Data/tidy_movies.csv")
```

## Stemming
```{r}
tidy_movies$word <- tokenize_word_stems(x = tidy_movies$word) %>% unlist()
write.csv(tidy_movies, file="Data/stemmed words.csv")
```

## Counting Words
```{r}
tidy_movies$Key <- paste0(tidy_movies$year, ":", tidy_movies$title)
tidy_movies <- as_tibble(tidy_movies)
words_count <- tidy_movies %>%
  group_by(Key) %>% 
  count(word, sort=TRUE) %>% 
  arrange(Key,desc(n))
```

## Manual Removal of words
### Removing very sparse and very frequent terms
```{r}
#' Creating Data Term matrix
words_count <- as_tibble(words_count)
words_count_dtm <- words_count %>% 
  cast_dtm(Key,word,n)
#' *Removing very sparse terms*
script_dtm_updated <- removeSparseTerms(words_count_dtm, 0.95) #if the words are only in 5% of movies they are deleted
sparse_terms<- tidy(words_count_dtm) %>% anti_join(tidy(script_dtm_updated),  by="term")#
#turning the document term matrix into a matrix
DF_removed_sparse_terms <- tidy(script_dtm_updated)


#' *Removing very frequent terms*
script_dtm_2 <- removeSparseTerms(words_count_dtm, 0.05)
DF_common_terms <- tidy(script_dtm_2)
DF_common_terms$term <- as.character(DF_common_terms$term)
#Making the AntiJoin
tidy_movies <- DF_removed_sparse_terms %>% anti_join(DF_common_terms,  by="term") #if the movies are in 95% of the movies they are deleted
```

### Removing words that are two or less characters (they don't give us anything)
```{r}
word_length <- str_length(tidy_movies$term)
word_length_2 <- tidy_movies[word_length==2,]
tidy_movies <- tidy_movies[!word_length==2, ]
tidy_movies <- data.frame(Key = tidy_movies$document
                          ,word = tidy_movies$term
                          ,n = tidy_movies$count)

write.csv(tidy_movies,file = "Data/word count synopsis.csv",row.names = FALSE)
rm(list = ls())
```

# Topic modelling
```{r}
#' *Data prep*
synopsis_words <- read.csv("Data/word count synopsis.csv")

top_words <- synopsis_words%>%
  group_by(word) %>% 
  summarise(sum=sum(n))

words_to_remove <- top_words[top_words$sum > 2000, ] %>% 
  select(1)

synopsis_words <- synopsis_words %>% anti_join(words_to_remove,  by="word") #if the word appear more often than 2000 times they are deleted

#' *Creating Data Term Matrix*
synopsis_words_dtm <- synopsis_words %>% 
  cast_dtm(Key,word,n)

#' *Doing LDAP*
library(doParallel)
CoreCount  <- makePSOCKcluster(detectCores()-1)
registerDoParallel(CoreCount)

  topics <- 50
  alpha <- 0.1
  delta <- 0.1
  synopsis_lda <- LDA(synopsis_words_dtm
                     ,k = topics #No. of topics
                     ,control = list(seed = 56, alpha = alpha, delta = delta)
                     ,method = "Gibbs")
  
  saveRDS(synopsis_lda,file = paste0("Data/synopsis_lda, T = ",topics,", A = ",alpha,", D = ",delta,'.rds'))

stopCluster(CoreCount)
registerDoSEQ()

lda_topics <- tidy(synopsis_lda, matrix = "beta")

write.csv(lda_topics, "Data/lda_topics.csv")

options(scipen = 999)
synopsis_lda_tidy <- tidy(synopsis_lda,matrix = "gamma")
synopsis_lda_tidy <- synopsis_lda_tidy %>% group_by(document)
synopsis_lda_tidy <- arrange(synopsis_lda_tidy,.by_group = TRUE)
synopsis_lda_tidy$gamma <- round(synopsis_lda_tidy$gamma,digits = 3)

write.csv(synopsis_lda_tidy,paste0("Data/synopsis_LDA_tidy, T = ",topics,", A = ",alpha,", D = ",delta,'.csv'), row.names = FALSE)
```

# Sentiment Analysis
## Bing
```{r}
#' *Load Data*
synopsis_words <- read.csv("Data/tidy_movies.csv")
synopsis_words$Key <- paste0(synopsis_words$year, synopsis_words$title)

#' *Bing*
bing_pr_year <- synopsis_words %>% 
  inner_join(get_sentiments("bing")) %>% 
  mutate(value = ifelse(sentiment == 'negative',yes = 0,no = 1)) %>% 
  group_by(year) %>% 
  summarise(sentiment = mean(value)) %>% 
  mutate(method = "BING")

### Plotting the sentiments pr year ###

#Defining X and Y
y <- bing_pr_year$sentiment
x <- bing_pr_year$year
  
#Making the plot
plot(x,y
     ,ylab = "Sentiment Score Pr. Year"
     ,xlab = "Year"
     ,main = "Sentiment Score per Year"
     ,pch = 20
     ,sub = "Bing")

#Adding a smoothing line
smooth <- loess(y~x)
xx <- seq(min(x), max(x), (max(x)-min(x))/1000)
f <- predict(smooth, xx, se = TRUE)
lines(x = xx,y = f$fit,col = "blue")

#Adding confidence intervals
ci <- f$se * qt(0.975, f$df)
cih <- f$fit + ci
cil <- f$fit - ci
xx <- c(xx, rev(xx))
yy <- c(cil, rev(cih))
polygon(xx, yy, col=rgb(0.1,0.1,0.1,0.25), border = NA)

legend("topright","Loess Fit",lty = 1,col = "blue",cex = 0.6,bg = "lightgrey")

grid()
```

## NRC
```{r}
#' *Grouping per years*
synopsis_words <- read.csv("Data/tidy_movies.csv")
synopsis_words$Key <- paste0(synopsis_words$year, synopsis_words$title)

tf <- 5
decades <- c(seq(from=1925, to= 2020, by = tf))
synopsis_words$decade <- decades[findInterval(synopsis_words$year, decades)]

#' *NRC Analysis*
sent_orig = unique(get_sentiments("nrc")$sentiment)
sent <- sent_orig[c(1:2,4:6, 8:10)]
countsent = length(sent)
nrc <- synopsis_words %>% 
  inner_join(get_sentiments("nrc")) %>% 
  group_by(decade) %>% 
  filter(sentiment %in% sent) %>% 
  count(sentiment)
sum <- nrc %>% group_by(decade) %>% summarise(sum = sum(n))
write.csv(sum, "Data/sum_nrc.csv")
write.csv(nrc,"Data/nrc.csv")
#' *Radarchart*
##' @1

decades <- setdiff(c(seq(from=min(unique(nrc$decade)), to= max(unique(nrc$decade)), by = tf)), 1933)

setdiff(1:85,seq(1,85,5))

for (i in decades) {
Y <- i
  n <- data.frame(matrix(c(round(
    nrc$n[nrc$decade == Y]/sum$sum[sum$decade == Y]*100
    ,1)), ncol = countsent))
  min <- data.frame(t(
      rep(min(round(
        nrc$n[nrc$decade == Y]/sum$sum[sum$decade == Y]*100
        ,1)),countsent)
    ))
  max <- data.frame(t(
      rep(max(round(
        nrc$n[nrc$decade == Y]/sum$sum[sum$decade == Y]*100
        ,1)),countsent)
    ))
  radar <- rbind(max, min, n)
  colnames(radar) <- c(nrc$sentiment[nrc$decade == Y])
  rownames(radar) <- c("max", "min", "decade")

  radarchart(radar
             , pcol = "deeppink3"
             , pfcol = scales::alpha("pink", 0.5), plwd = 2, plty = 1
             , cglcol = "grey", cglty = 1, cglwd = 0.8
             , title = paste0("Timeframe ", Y, " - ", Y+tf)
             , caxislabels=seq(min[1,1],max[1,1],((max[1,1]-min[1,1])/4))
             , axislabcol="grey"
             , axistype=4
  )
}

##' @2

decades <- setdiff(c(seq(from=min(unique(nrc$decade)), to= max(unique(nrc$decade)), by = tf)), 1933)

setdiff(1:85,seq(1,85,5))

for (i in decades) {
Y <- i
  n <- data.frame(matrix(c(round(
    nrc$n[nrc$decade == Y]/sum$sum[sum$decade == Y]*100
    ,1)), ncol = countsent))
  min <- data.frame(t(rep(4,8)))
  max <- data.frame(t(rep(22,8)))
  radar <- rbind(max, min, n)
  colnames(radar) <- c(nrc$sentiment[nrc$decade == Y])
  rownames(radar) <- c("max", "min", "decade")

  radarchart(radar
             , pcol = "deeppink3"
             , pfcol = scales::alpha("pink", 0.5), plwd = 2, plty = 1
             , cglcol = "grey", cglty = 1, cglwd = 0.8
             , title = paste0("Timeframe ", Y, " - ", Y+tf)
                                , caxislabels=seq(0,max[1,1],(max[1,1]/4))
                   , axislabcol="grey"
                   , axistype=4
  )
}
```

